A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/02_Materials_and_Methods.Rmd
better figure captions

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database. The red frame indicates the research area.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_regions.jpeg}
\caption{\label{map_regions}Circular, artificial regions (\textbf{A}) and spatial distance network with classified distance values (\textbf{B}).}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database. The classes of the variable \textit{burial type} are distinguished by colour, the ones of \textit{burial construction} by shape. The red frame indicates the research area. The Map projection is EPSG:102013 and the base layer (land, rivers, lakes) data is taken from the Natural Earth project (\url{www.naturalearthdata.com}).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_regions.jpeg}
\caption{\label{map_regions}Circular, artificial regions (\textbf{A}) and spatial distance network with classified distance values (\textbf{B}). The map layout is the same as in Figure \ref{map_graves}.}
\end{figure}
